\documentclass[addpoints]{exam}
\usepackage{amsmath, amsfonts}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{titling}

% Header and footer.
\pagestyle{headandfoot}
\runningheadrule
\runningfootrule
\runningheader{CS 212, Fall 2022}{HW 1: Regular Languages}{\theauthor}
\runningfooter{}{Page \thepage\ of \numpages}{}
\firstpageheader{}{}{}

\boxedpoints

\title{Homework 1: Regular Languages--Automata and Expressions}
\author{ungraded} % <=== replace with your team name
\date{CS 212 Nature of Computation\\Habib University\\Fall 2022}

\begin{document}
\maketitle

\begin{questions}

\question For each of the languages specified below, provide the formal specification and the state diagram of a finite automaton that recognizes it. 
  \begin{parts}
  \part[5] $L= \{w\in \{0,1\}^* \mid n_0(w)=2, n_1(w)\leq 5 \}$   where $n_x(w)$ denotes the counts of $x$s in $w$.
  \part[5] $(((00)^*(11))\cup 01)^*$.
  \end{parts}

  Please see \href{https://www3.nd.edu/~kogge/courses/cse30151-fa17/Public/other/tikz_tutorial.pdf}{this guide} for help on drawing state diagrams.
  
\question[5] Below is the transition table of a finite automaton. $\implies$ indicates the starting state, and $*$ indicates accepting states. Provide a regular expression for the language recognized by this automaton.
  \[
  \begin{array}{r|cc}
    & 0 & 1 \\\hline
    p & \{ q \} & \emptyset \\
    \implies q & \{ q \} & \{ q, r \} \\
    *r & \emptyset & \{ s \} \\
    *s & \emptyset & \emptyset \\
  \end{array}
  \]
  
\question
  \begin{parts}
  \part[5] Suggest regular languages $L_1$ and $L_2$ over $\{0,1\}$ such that
  \begin{enumerate}
  \item $L_1\not\subseteq L_2$,
  \item $L_2\not\subseteq L_1$, and
  \item $(L_1\cup L_2)^* = L_1^* \cup L_2^*$
  \end{enumerate}
  \part[5] Prove or disprove whether condition 3 above holds for any regular languages, $L_1$ and $L_2$.
  \end{parts}

\question[5] In class, we talked about the closure of the class, $A$, of regular languages under the union, concatenation, and star operations. In this question, we want to explore whether $A$ is also closed under intersection. That is, does the following hold?
  \[
    L_1\in A \land L_2\in A \implies L_1 \cap L_2\in A
  \]

  We want to go about it as follows. The expression, $L_1 \cap L_2$, can be transformed using DeMorgan's law to an equivalent one involving union, for which closure is known, and another operation. Show whether $A$ is closed under this operation, and use your result to argue about the closure of $A$ under intersection.

\question[5] We now want to explore the closure of the class, $A$, of regular languages under the operation, $mix$, which is defined as follows.
  \begin{itemize}
  \item Given strings, $u$ and $v$, both of length $n$, $mix(u,v) = u_1v_1u_2v_2\ldots u_nv_n$.
  \item Given languages, $L_1$ and $L_2$, $mix(L_1,L_2) = \{mix(u,v) \mid u\in L_1, v\in L_2, |u| = |v|\}$.
  \end{itemize}
  Is $A$ closed under $mix$? Justify your answer.
  
\end{questions}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
